%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% CV Jakša Tomović 06/2019 %%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\PassOptionsToPackage{dvipsnames}{xcolor}
\documentclass[10pt,a4paper]{altacv}

%Layout
\geometry{
left=1cm,
right=9cm,
marginparwidth=6.8cm,
marginparsep=1.2cm,
top=1.25cm,
bottom=1.25cm,
footskip=2
\baselineskip}

%Packages
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[default]{lato}
\usepackage[hidelinks]{hyperref}
\usepackage{mdframed}
\usepackage{varwidth}

%Colors
\definecolor{accent}{HTML}{000e17}
\definecolor{heading}{HTML}{000e17}
\definecolor{emphasis}{HTML}{696969}
\definecolor{body}{HTML}{01415f}

\colorlet{heading}{heading}
\colorlet{accent}{accent}
\colorlet{emphasis}{emphasis}
\colorlet{body}{body}

\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}
%

\begin{document}

\name{Iskander Andrews}
\tagline{Software Engineer | Blockchain Developer}
%\photo{2.5cm}{BrunoAlves}
\personalinfo{
    \email{iskander.s.andrews@gmail.com}
    \phone{(+20) 155 064 8806}
%    \mailaddress{SR Njemačke 6, 10000}
    \linkedin{\href{https://www.linkedin.com/in/iskander-andrews-99638313a/}{\custombold{LinkedIn}}}
    \github{\href{https://github.com/iskanderandrews}{\custombold{GitHub}}}
    \location{Egypt}
}

%
\begin{fullwidth}
\makecvheader
\end{fullwidth}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Education %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\cvsection[page1sidebar]{Education {\faUniversity}}

\cvevent{Bachelor in Computer Science}{Faculty of computer and Artificial Intelligence, Helwan University
\\
{\footnotesize{GPA: 2.88} \hspace{1em} Grade: Very Good} \hspace{1em}
{\faCertificate} \hyperlink{https://drive.google.com/file/d/1_t0bm3bfhOqXAp67HTInoRzFYic2FVsn/view?usp=sharing}{Student Transcript}
}{Oct 2015 - June 2019}{Egypt}

\begin{itemize}
\item Hands on experience and Team Leader on building a Desktop Linux Application for Graduation Project program, which is:
\end{itemize}

%%%%%%%%%%%%%
%Project 3
%%%%%%%%%%%%%
\begin{mdframed}

\cvprojectevent{\href{https://github.com/KirollosNasr/Smart-Terminal}{Linux Assistant - Smart Terminal \faLinux}}{April 2019 -- June 2019}
\begin{itemize}
  \item \small{In this Graduation Project, we have implemented an assistant agent for Linux newcomers that helping them in dealing with such an operating system. Also, helping in controlling Linux with natural language -English-. We developed this application by Machine Learning and Speech Recognition. Also by Natural Language Processing algorithms. We have discussed this project under the supervision of  \href{http://fcih.helwan.edu.eg/index.php/en/is-department/faculty-members-is/35-dr-marwa-salah}{\textit{Dr. Marwa Salah}}. We have got A+ Grade.}

\end{itemize}
\cvtag{JavaScript}
\cvtag{ElectronJS}
\cvtag{Python}
\cvtag{NLP}
\cvtag{KNN}
\end{mdframed}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Experience %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\cvsection{Experience}

%%%%%%%%%%%%%
%Experience 1
%%%%%%%%%%%%%
\cvmainevent{Geometric Energy Corp.}{\href{https://www.geometricenergy.ca/}{Website}}{\href{https://www.linkedin.com/company/geometric-energy-corporation/}{LinkedIn}}{\href{https://github.com/GeometricEnergyCorporation}{GitHub}}{Canada}

\cvsubsubevent{}
\cvsubevent{Software Engineer | Blockchain Developer - Remote}{November 2019 -- Present}

\begin{itemize}
\item Gaining experience from working on \href{https://coinstreet.partners/}{CoinStreet} Project, which is a Decentralized Investment Banking (DIB) and digital asset consultancy solution, enabling business eco-system for the new era of digital economy.
\end{itemize}

\begin{itemize}
\item Hands on experience on building a Dfini Decentralized Investment Bank (DIB) project, which is:
\end{itemize}

\begin{mdframed}
%%%%%%%%%%%%%
%Project 1
%%%%%%%%%%%%%
\cvprojectevent{\href{https://dfini.com/}{DFINI - DIB}}{May 2020 -- In progress }
\begin{itemize}
  \item \small{A Decentralized Finance (DFINI) A solution provider focused on the decentralized finance sector. We develop decentralized finance solutions that allow established institutions to adopt distributed ledger technology, and provide open finance platforms that empower individuals around the world to engage with new and restructured financial systems.} 
\end{itemize}

\cvtag{JavaScript}
\cvtag{ReactJS}
\cvtag{NodeJS}
\cvtag{web3JS}
\cvtag{ERC 20}
\cvtag{Solidity}
\end{mdframed}

\divider

\cvmainevent{Blockboard}{\href{https://blockboard.weebly.com/}{Website}}{\href{https://www.linkedin.com/company/block-board/about/}{LinkedIn}}{\href{https://github.com/blockboard}{GitHub}}{Egypt}

\cvsubevent{Full Stack Blockchain Developer \faEthereum}{January 2020 -- Present}

%%%%%%%%%%%%%
%Project 2
%%%%%%%%%%%%%
\begin{itemize}
\item Hands on experience on building NFTs with it's marketplace which is:
\end{itemize}

\newpage

\cvsection[page2sidebar]{Experience}

\begin{mdframed}
\cvprojectevent{\href{https://www.cryptoweirdos.space/}{CryptoWeirdos}}{January 2020 -- March 2020}

\begin{itemize}
  \item A Non-Fungible Tokens (NFT) project on top of Ethereum with MetaMask login system. 
  \item First I implemented two smart-contracts according to ERC\-721 standard. Then another smart-contract for the MarketPlace of these tokens,
  \item A server-side RestAPI using NodeJS and ExpressJS for handling tokens metadata and storing it into MongoDB Atlas and IPFS for storing images, deployed on Heroku. A client-side with ReactJS and Material-UI liberary, deployed on Netlify.
\end{itemize}
\begin{itemize}
   
\end{itemize}
\begin{itemize}
\cvtag{JavaScript}
\cvtag{ReactJS}
\cvtag{NodeJS}
\cvtag{ExpressJS}
\cvtag{MongoDB}
\cvtag{Solidity}
\cvtag{IPFS}
\cvtag{ERC 721}
\cvtag{Web3JS}
\cvtag{Truffle}
\cvtag{OpenZepplin}
\end{itemize}
\end{mdframed}

\begin{itemize}
\item Hands on experience on building a Decentralized finance App on Ethereum (DeFi) project, which is:
\end{itemize}

\begin{mdframed}
%%%%%%%%%%%%%
%Project 1
%%%%%%%%%%%%%
\cvprojectevent{DeFi \faEthereum}{April 2020 -- In progress }
\begin{itemize}
  \item A Decentralized Finance (DeFi) project on top of Ethereum, which is mainly for issuing ERC20 tokens on Ethereum network according to \href{https://github.com/ethereum/eips/issues/20}{ERC20 standards}. Also the allowance for exchanging these tokens.
  \item We're now in the analysis and design phase, and have finished our first sprint which is ERC20 Token Generator. 
\end{itemize}

\cvtag{JavaScript}
\cvtag{ReactJS}
\cvtag{NodeJS}
\cvtag{ExpressJS}
\cvtag{MongoDB}
\\
\cvtag{ERC 20}
\cvtag{Hardware Wallet}
\cvtag{IPFS}
\cvtag{\href{https://sia.tech/}{Sia}}
\cvtag{Solidity}
\cvtag{ICO / STO}
\end{mdframed}

\begin{itemize}
\item Hands on experience on building a simple Timestamping project, which is:
\end{itemize}

\begin{mdframed}
%%%%%%%%%%%%%
%Project 1
%%%%%%%%%%%%%
\cvprojectevent{Art-Stamp}{May 2020 -- In progress }
\begin{itemize}
  \item A simple project for Timestamping a digital documents in distributed ledgers, and Ethereum Blockchain.   
\end{itemize}

\cvtag{JavaScript}
\cvtag{ReactJS}
\cvtag{NodeJS}
\cvtag{IPFS}
\cvtag{\href{https://sia.tech/}{Sia}}
\cvtag{Solidity}
\end{mdframed}

\cvsubevent{Blockchain Developer Intern \faEthereum}{October 2019 -- December 2019}

\begin{itemize}
\item In this Internship, I've learned about different Blockchains, like Ethereum, and Blockstack from a high-level. We focused on learning a lot about Ethereum Network with the concept of Smart-Contracts, and Tokenization, and how to build a client-side app with ReactJS, and how to build a RESTFul APIs with NodeJS. After that, we began to experiment and build projects on Blockchain.
\end{itemize}
\divider

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Reference %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Reference}
\cvreference{\href{https://www.linkedin.com/in/shadymichael/} {Shady A. Micheal}}{Founder at Blockboard | Founder at S+ studio}

\begin{itemize}
  \item \faEnvelope{\hspace{5pt}shady.a.michael@gmail.com }
\end{itemize}


\end{document}
